\documentclass{standalone}

\begin{document}
	It is somewhat well known that in the early 2000s the web began to transition from static pages into web-applications, i.e. those powered by user-generated content and dynamic HTML. This new form of the web was coined Web 2.0 \parencite{Web20}. Over the past few years, the potential of these web-applications have evolved massively. In particular, many new technologies, such as those specified within HTML5, have been introduced into the average web-browser. These technologies have broadened the capabilities of a web-application; making them an incredibly viable medium for many software projects. In the past, browser-based video-games required the use of third-party browser-extensions, such as Adobe Flash. However, with the aforementioned improvements, there now exists curiosity regarding the feasibility of implementing a browser-based video-game using solely the technologies natively available within the web-browser.

	Due to those reasons, for this project we are to develop a multiplayer implementation of the video-game Tron. It shall feature a computer opponent, powered by some artificial intelligence enabling it to compete against able-bodied computer users. The focus of the project is not to develop a fully-polished, consumer-ready product; but instead to create a fully functioning prototype, demonstrating the use of various video-game design techniques and the feasibility of their implementation within a web-application. 

	The web-application will support a server capable of running, and arbitrating, multiple simultaneously game lobbies, each holding their own game instance. A group of users are then able to connect to a particular game lobby, in order to become players of the game instance and thus able to compete against one-another over a network. A variety of networking techniques will be employed to improve the user-experience, by diminishing  perceptible latency.

	The intention of the artificial intelligence, controlling the computer opponent, is not to play the game neigh perfecting, besting the majority of human combatants, but instead to act with human-like strategy and behaviour; remaining both challenging, but possible for an average user to beat - keeping the game enjoyable. This will entail the use of simulation-based techniques and concurrency.
\end{document}